CKY Parsing With Independence Constraints

### 2015-02-28 paper.tex
Minor edits

In order to find the best configuration of features for the
classifier, and to evaluate the proposed POS levels, we tested the
classifier using several different combinations. Selected results are
shown in Table \ref{tbl:feature-evaluation}. In the "Features" column,
$p$ denotes the local features, and $P_{l}$ denotes the global
features from POS level $l$.

There are several things worth noting in these results. First, neither
local nor global features are sufficient alone; it appears that local
features promote precision, while global features promote recall.
Second, examining the cases where global features are limited to a
single POS level, it is apparent that each POS level has a different
effect on precision and recall, thus confirming that the classifier is
able to extract different signals from the different POS levels, as
intended. Finally, combining all POS levels together actually reduces
accuracy, likely due to overfitting (although see the discussion of
the kernel classifier).

@@

\subsection{Polynomial Kernel}
\label{sec-5-3}

>>>>

In order to find the best configuration of features for the
classifier, and to evaluate the proposed POS levels, we tested the
classifier using several different combinations. Selected results are
shown in Table \ref{tbl:feature-evaluation}. In the ``Features'' column,
$p$ denotes the local features, and $P_{l}$ denotes the global
features from POS level $l$.

There are several things worth noting in these results. First, neither
local nor global features are sufficient alone; it appears that local
features promote precision, while global features promote recall.
Second, examining the cases where global features are limited to a
single POS level, it is apparent that each POS level has a different
effect on precision and recall, thus confirming that the classifier is
able to extract different signals from the different POS levels, as
intended. Finally, combining all POS levels together actually reduces
accuracy, likely due to overfitting (although see the discussion of
the kernel classifier below).

@@

\subsection{Polynomial Kernel}
\label{sec:results-poly}
